---
title: "Assignment 3"
author: "PLSC 31101"
date: "Fall 2020"
output: html_document
---

## Assignment 3

- __Assigned__: TBD.
- __Due__: TBD.

For this assignment, we'll be working with the country-year data introduced in the last assignment. As a reminder, the dataset contains the following variables:

* `year`: Year.
* `ccode`: Country numerical code.
* `country`: Country name.
* `idealpoint` UN Ideal point.
* `polity2`: Polity2 score of regime type (from Polity IV).
* `physint`: Physical Integrity Rights score (from CIRI dataset).
* `speech`: Speech Rights score (from CIRI).
* `gdp.pc.wdi`: GDP per capita (from World Bank).
* `pop.wdi`: Population (from World Bank).
* `amnesty`: Political Terror Scale using Amnesty International reports (from Political Terror Scale project).
* `cinc`: Composite Index of Military Capabilities (Correlates of War).
* `region`: Geographic region.

#### 1. Getting Started {-}

__1.1 Read `data/country-year.csv` into R, using a relative path. Store it in an object called `dat`.__

```{r}
# YOUR CODE HERE
```

#### 2. Plotting {-}

__2.1 Write code that reproduces "plots/Plot_1.jpeg". (No need to write the file.)__

```{r}
# YOUR CODE HERE
```

__2.2 Write code that reproduces "plots/Plot_2.jpeg". (No need to write the file.)__

```{r}
# YOUR CODE HERE
```

__2.3 Write code that reproduces "plots/Plot_3.jpeg". (No need to write the file.)__

__Hint: The fall-inspired colors are #771C19, #E25033, #F27314, #F8A31B__

```{r}
# YOUR CODE HERE
```

__2.4 Write code that reproduces "plots/Plot_4.jpeg". (No need to write the file.)__

```{r}
# YOUR CODE HERE
```

#### 3. Models {-}

__3.1 Write code that reproduces the model summary table "reg_table.txt" (and writes the file).__

```{r}
# YOUR CODE HERE
```

