---
title: "Assignment 3"
author: "PLSC 31101"
date: "Fall 2020"
output: html_document
---

## Assignment 3

- __Assigned__: Oct 19, 2020
- __Due__: Oct 26, 2020

For this assignment, we'll be working with the country-year data introduced in the last assignment. As a reminder, the dataset contains the following variables:

* `year`: Year.
* `ccode`: Country numerical code.
* `country`: Country name.
* `idealpoint` UN Ideal point.
* `polity2`: Polity2 score of regime type (from Polity IV).
* `physint`: Physical Integrity Rights score (from CIRI dataset).
* `speech`: Speech Rights score (from CIRI).
* `gdp.pc.wdi`: GDP per capita (from World Bank).
* `pop.wdi`: Population (from World Bank).
* `amnesty`: Political Terror Scale using Amnesty International reports (from Political Terror Scale project).
* `cinc`: Composite Index of Military Capabilities (Correlates of War).
* `region`: Geographic region.

## 1. Getting Started

### 1.1 

Read `data/country-year.csv` into R, using a relative path. Store it in an object called `dat`.

```{r}
# YOUR CODE HERE
```

## 2. Plotting 

### 2.1 

Write code that reproduces `plots/Plot_1.jpeg`. (No need to write the file.)

```{r}
# YOUR CODE HERE
```

### 2.2 

Write code that reproduces `plots/Plot_2.jpeg`. (No need to write the file.)

```{r}
# YOUR CODE HERE
```

### 2.3 

Write code that reproduces `plots/Plot_3.jpeg`. (No need to write the file.)

Hint: The fall-inspired colors are #771C19, #E25033, #F27314, #F8A31B

```{r}
# YOUR CODE HERE
```

## 3. Models

### 3.1 

Write code that reproduces the model summary table `regression-table.txt` (and writes the file).

```{r}
# YOUR CODE HERE
```

## 4. Extra Bonus Challenge

Using the code from chapter 13.2 as a guide, plot the marginal effects of each term in the model below, EXCLUDING the intercept and the `ccode` dummy variables.

```{r}
# estimate model
mod <- lm(physint ~ polity2 + idealpoint + log(gdp.pc.wdi) + log(pop.wdi) + factor(ccode), data = dat)

# YOUR CODE HERE
```

