---
title: "Assignment 3 Solutions"
author: "PLSC 31101"
date: "Fall 2020"
output: html_document
---

## Assignment 3

- __Assigned__: TBD.
- __Due__: TBD.


For this assignment, we'll be working with the country-year data introduced in the last assignment. As a reminder, the dataset contains the following variables:

* `year`: Year.
* `ccode`: Country numerical code.
* `country`: Country name.
* `idealpoint` UN Ideal point.
* `polity2`: Polity2 score of regime type (from Polity IV).
* `physint`: Physical Integrity Rights score (from CIRI dataset).
* `speech`: Speech Rights score (from CIRI).
* `gdp.pc.wdi`: GDP per capita (from World Bank).
* `pop.wdi`: Population (from World Bank).
* `amnesty`: Political Terror Scale using Amnesty International reports (from Political Terror Scale project).
* `cinc`: Composite Index of Military Capabilities (Correlates of War).
* `region`: Geographic region.

#### 1. Getting Started {-}

__1.1 Read `data/country-year.csv` into R, using a relative path. Store it in an object called `dat`.__

```{r}
library(tidyverse)
library(stargazer)
dat <- read.csv("Data/country-year.csv", stringsAsFactors = F)
```

#### 2. Plotting {-}

__2.1 Write code that reproduces "plots/Plot_1.jpeg". (No need to write the file.)__

```{r}
# Density of population
d <- density(log(dat$pop.wdi), na.rm = T, bw = .2)
plot(d, main = "Summary of Population (Logged)") 
abline(h = max(d$y), v = 16.09, lty = 2) 
```

__2.2 Write code that reproduces "plots/Plot_2.jpeg". (No need to write the file.)__

```{r}
# get summary data
country_means <- dat %>%
  filter(!is.na(region)) %>%
  group_by(country) %>%
  summarise(gdp = mean(gdp.pc.wdi, na.rm = T),
            polity = mean(polity2, na.rm = T),
            cinc = mean(cinc, na.rm = T),
            region = region[1])

# plot
ggplot(country_means, aes(x = polity, y = log10(gdp))) +
  geom_point(aes(color = region)) +
  #scale_y_log10() +
  geom_smooth(color="red", fill="red") + 
  ylab("Mean GDP (Logged) ") +
  xlab("Mean Polity Score") +
  ggtitle("Average Polity Score by GDP, 1979-2014") 
```

__2.3 Write code that reproduces "plots/Plot_3.jpeg". (No need to write the file.)__

__Hint: The fall-inspired colors are #771C19, #E25033, #F27314, #F8A31B__

```{r}
# military capabilities
top_cinc <- country_means %>%
  top_n(10, cinc)

# Fall theme
rhg_cols = c("#771C19","#E25033","#F27314", "#F8A31B")

# plot
ggplot(top_cinc, aes(reorder(country, cinc), cinc, fill = region)) +
  geom_col() +
  theme(axis.text.x=element_text(size = 7, angle=45, hjust=1)) +
  ylab("Composite Index of Military Capabilities") +
  xlab("Country") +
  ggtitle("Top 10 Military Capabilities, in Fall Colors") +
  scale_fill_manual(values = rhg_cols)
```

__2.4 Write code that reproduces "plots/Plot_4.jpeg". (No need to write the file.)__

```{r}
# prepare data
year_means <- dat %>%
  filter(!is.na(region)) %>%
  group_by(year, region) %>%
  summarise(gdp = mean(gdp.pc.wdi, na.rm = T),
            polity = mean(polity2, na.rm = T),
            physint = mean(physint, na.rm = T)) 

# plot
ggplot(year_means, aes(x = year, y = polity, color = region)) +
  geom_line(size=2) +
  ylab("Average Polity Score") +
  xlab("Year") +
  ggtitle("Average Polity Score Over Time")
```

#### 3. Models {-}

__3.1 Write code that reproduces the model summary table "reg_table.txt" (and writes the file).__

```{r}
mod.1 <- lm(physint ~ polity2, data = dat)
mod.2 <- lm(physint ~ polity2 + log(gdp.pc.wdi), data = dat)
mod.3 <- lm(physint ~ polity2 + log(gdp.pc.wdi) + region, data = dat)

stargazer(mod.1, mod.2, mod.3, title = "Regression Results", type = "text", 
          covariate.labels  = c("Polity2", "GDP per capita, logged", "Asia", "Eastern Europe", "Latin America", "MENA", "West", "Constant"), 
          dep.var.labels = "DV: Physical Integrity",
          omit = "Constant", 
          keep.stat="n", style = "ajps",
          out = "reg_table.txt")
```

